### 2020-04-02 draft.tex
MEs

\section{Introduction}
A polynomial functor $P : \Set \to \Set$ is a sum of representables
\begin{equation}\label{eqn.poly}
P(X) := \sum_{b \in B} X^{E_b}
\end{equation}
and therefore depends on a family of sets $E_b$ depending on $b\in B$. This data is known
in the computer science literature as a ``container'', but since such an indexed
family of sets can be represented by as a function
\[
  \begin{tikzcd}
    E \arrow[d, "\pi"] \\
    B
  \end{tikzcd}
\]
we will refer to it as a \emph{bundle}. We think of a bundle as a categorified
Young diagram:

@@

As a corollary, any $\pi : \downarrow \to \Set$ equals the composite
$$\downarrow \xto{\sigma} \downarrow\op \xto{!_0\op} \Set\op \xto{!_{(-)}\op}
(\Set^{\downarow})\op \xto{\Set^{\downarrow}(-, \pi)} \Set$$
by the Yoneda lemma.
\end{lem}
\begin{proof}
One checks directly.
\end{proof}

>>>>

\section{Introduction}
A polynomial functor $P : \Set \to \Set$ is a sum of representables
\begin{equation}\label{eqn.poly}
P(X) := \sum_{b \in B} X^{E_b}
\end{equation}
where the family of sets $E_b$ depends on $b\in B$. This data is known
in the computer science literature as a ``container'', but since such an indexed
family of sets can be represented by as a function
\[
  \begin{tikzcd}
    E \arrow[d, "\pi"] \\
    B
  \end{tikzcd}
\]
we will refer to it as a \emph{bundle}. We think of a bundle as a categorified
Young diagram:

@@

As a corollary, any $\pi : \downarrow \to \Set$ equals the composite
$$\downarrow \xto{\sigma} \downarrow\op \xto{!_0\op} \Set\op \xto{!_{(-)}\op}
(\Set^{\downarrow})\op \xto{\Set^{\downarrow}(-, \pi)} \Set$$
by the Yoneda lemma.
\end{lem}
\begin{proof}
One checks directly.
\end{proof}
